Classless Java

### 2016-03-22 OOPSLA16/sections/FutureWork.tex
Text in Section 4. Code style.

As shown by Ferruccio in [...] interfaces are enough to support privateness by a
 variation of the facade pattern:
\begin{lstlisting}
@Obj interface InternalData implements ExposedData{/*all the methods*/}//package visibility
public interface ExposedData{
  /*just the exposed interface*/
  static ExposedData of(...){return InternalData.of(...);}  }
\end{lstlisting}

>>>>

As shown by Ferruccio in [...] interfaces are enough to support privateness by a
 variation of the facade pattern:
\begin{lstlisting}
@Obj interface InternalData implements ExposedData {
    /*all the methods*/} //package visibility
public interface ExposedData {
  /*just the exposed interface*/
  static ExposedData of(...) {
    return InternalData.of(...);}  }
\end{lstlisting}
